---
title: "Data Science for Business Decisions"
author: "Mohammed Ayubsha"
date:  "2 February,2021"
output: html_document
---
**Task:**Using the given data (full_grouped.csv), create an animated graph that showcases the top 15 countries in terms of death date-wise.

# Part 1

## Understanding COVID_19 dataset

*Reading the csv file and looking at summary*
```{r}
Data <-read.csv ("C:/Users/Abu Ayub/Downloads/full_grouped.csv", header =T)
str(Data)
summary(Data)
```
**Dataset:**The variables are Date,Country.Region,Confirmed,Deaths,Recovered,Active,New.cases,New.deaths,New.recovered and WHO.Region.

# Part 2

## Creating Animated plot

*Loading the required libraries*
```{r}

library(tidyverse)
library(gganimate)
```

*Obtaining names of top 15 countries in terms of highest number of deaths in descending order*
```{r}
deathdata <- Data %>%
  group_by(Date) %>%
  mutate(rank = rank(-Deaths),
         Value_lbl = paste0(" ",Deaths)) %>%
  group_by(Country.Region) %>% 
  filter(rank <=15) %>%
  ungroup()
```

*Using ggplot to create plot with required settings and labels*
```{r}
staticplot = ggplot(deathdata, aes(rank, group = Country.Region, 
                                      fill = as.factor(Country.Region), color = as.factor(Country.Region))) +
  geom_tile(aes(y = Deaths/2,height = Deaths,width = 0.9), alpha = 0.8, color = NA) +
  geom_text(size=8,aes(y = 0, label = paste(Country.Region, " ")), vjust = 0.2, hjust = 1) +
  geom_text(size=8,aes(y=Deaths,label = Value_lbl, hjust=0)) +
  coord_flip(clip = "off", expand = FALSE) +
  scale_y_continuous(labels = scales::comma) +
  scale_x_reverse() +
  guides(color = FALSE, fill = FALSE) +
  theme(axis.line=element_blank(),
        axis.text.x=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks=element_blank(),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        legend.position="none",
        panel.background=element_blank(),
        panel.border=element_blank(),
        panel.grid.major=element_blank(),
        panel.grid.minor=element_blank(),
        panel.grid.major.x = element_line( size=.1, color="grey" ),
        panel.grid.minor.x = element_line( size=.1, color="grey" ),
        plot.title=element_text(size=27, hjust=0.5, face="bold", colour="black", vjust=-1),
        plot.subtitle=element_text(size=18, hjust=0.5, face="italic", color="grey"),
        plot.caption =element_text(size=8, hjust=0.5, face="italic", color="grey"),
        plot.background=element_blank(),
        plot.margin = margin(2,4, 2, 12, "cm"))
```

*creating an Animation plot*
```{r}
animplot = staticplot + transition_states(Date, transition_length = 4, state_length = 1) +
  view_follow(fixed_x = TRUE)  +
  labs(title = 'Total Death Cases : {closest_state}',  
       subtitle  =  "Top 15 Countries")
```

*Giving the preferred setting and saving the file as Death_Cases.gif*
```{r}
animate(animplot, 300, fps = 20,  width = 1100, height = 800, 
        renderer = gifski_renderer("Death_Cases.gif"))
```